Windowed least-squares model reduction for dynamical systems

### 2019-10-16 section4/numerical_methods.tex
small changes

In the present context, we investigate both direct and indirect methods to solve \methodAcronym\ with \spatialAcronym\ trial
subspaces. In particular, we consider:
\begin{itemize} \item \textit{Direct methods (discretize-then-optimize)}: A direct approach leveraging linear multistep methods to directly solve the optimization problem~\eqref{eq:obj_gen_slab}.
Section~\ref{sec:direct} outlines this approach.
\item \textit{Indirect methods (optimize-then-discretize)}: An indirect
	approach leveraging the forward--backward sweep algorithm to solve the
		Euler--Lagrange equations~\eqref{eq:lspg_continuous}--\eqref{eq:lspg_bcs}.
Section~\ref{sec:indirect} outlines this technique.
\end{itemize} 
We note that a variety of other approaches exist, and their investigation
comprises the subject of future work.

>>>>

In the present context, we investigate both direct and indirect methods to solve \methodAcronym\ with \spatialAcronym\ trial
subspaces. In particular, we consider:
\begin{itemize} \item \textit{Direct methods (discretize-then-optimize)}: A
			direct approach that leverages linear multistep methods to directly solve the optimization problem~\eqref{eq:obj_gen_slab}.
Section~\ref{sec:direct} outlines this approach.
\item \textit{Indirect methods (optimize-then-discretize)}: An indirect
	approach that leverages the forward--backward sweep algorithm to solve the
		Euler--Lagrange equations~\eqref{eq:lspg_continuous}--\eqref{eq:lspg_bcs}.
Section~\ref{sec:indirect} outlines this technique.
\end{itemize} 
We note that a variety of other approaches exist, and their investigation
comprises the subject of future work.

### 2019-10-16 section4/spatial_numerical.tex
updated figures
small changes

\subsection{\spatialAcronym: direct solution approach}\label{sec:direct} 
\KTC{HERE}
\KTC{Does the time grid definted in this section have any relationship to the
time grid used for time discretization? Haven't gotten past HERE below, but
wanted to check (maybe it's made clear later).}
\EP{This time grid becomes the time discretization over each window. At this point in the paper, 
there is no notion of a time grid for \methodAcronym}

Direct approaches solve the optimization problem~\eqref{eq:tclsrm} by
``transcribing" the infinite dimensional optimization problem into a finite
dimensional one by discretizing the state and objective functional in time.
The minimization problem is then reformulated as a (non)linear programming, or
optimization, problem. A variety of direct solution approaches exist, 
including collocation approaches, spectral  methods, and genetic algorithms.

In the present context, the most straightforward direct solution approach consists of the 
following steps: (1) numerically discretize the FOM ODE (and hence the \textit{integrand} of~\eqref{eq:obj_gen_slab}) and 
(2) select a numerical quadrature rule to evaluate the \textit{integral} in~\eqref{eq:obj_gen_slab}.
To this end, we start by defining a discrete time grid 
over each window by introducing
$\nstepsArg{n}+1$ strictly increasing time instances described by
$\{\timeWindowArg{n}{i}\}_{i=0}^{\nstepsArg{n}}$ with
%\KTC{use cdots, not
%hdots or ldots. Don't use $\defeq$ for the first and last times; these are
%just equalities, i.e., you happen to set them equal to those values, but they
%aren't identically the same:}
\begin{align}
&\timeWindowArg{n}{0} \le \cdots \le \timeWindowArg{n}{\nstepsArg{n}} , \label{eq:timegrid1} \;
\timeWindowArg{n}{0} = \timeStartArg{n},\;
\timeWindowArg{n}{\nstepsArg{n}} = \timeEndArg{n} . 
%\timeWindowArg{n}{0} = \timeStartArg{n}, \timeWindowArg{n}{\nstepsArg{n}} =
%\timeEndArg{n}
\end{align}
Figure~\ref{fig:slab_fig2} depicts this discretization.
We now outline the direct solution approach for linear-multistep schemes; we note that the formulation for
other time-stepping methods (e.g., Runge--Kutta) follows closely. 
\begin{figure} 
\begin{centering} 
\includegraphics[trim={0.0cm 5cm 0cm 3cm},clip,width=1.0\textwidth]{figs/time_grid_timesteps.pdf} 
	\caption{Depiction of the $\nstepsArg{n}+1$ time instances over each window. In the figure, $\nstepsArg{n} = 3$ for all $n$.} 
\label{fig:slab_fig2} 
\end{centering} 
\end{figure}
%We now outline several commonly employed temporal discretization 
%schemes, specifically linear multistep and collocation (Runge--Kutta) methods, that leverage this time-grid to discretize the FOM ODE and 
%objective functional.

@@

\EP{This section has the double superscript. We could make one of these a subscript, but then need to change the algorithms a bit as 
I use subscripts to denote iterations. Either is fine}

@@

\subsection{\spatialAcronym: indirect solution approach}\label{sec:indirect}
In contrast to the direct approach,
indirect methods ``indirectly" solve the minimization
problem~\eqref{eq:tclsrm} by solving the Euler--Lagrange equations. The
system given by the Euler--Lagrange equations~\eqref{eq:lspg_continuous}--\eqref{eq:lspg_adjoint} comprises a coupled two-point boundary value
problem. A variety of techniques have
been devised to solve two-point boundary value problems of this type. These
techniques include shooting methods, multiple shooting
methods~\cite{multiple_shooting}, and the forward--backward sweep
method~\cite{fbs} (FBSM).  This work explores using the FBSM.

>>>>

\subsection{\spatialAcronym\ trial subspaces: direct solution approach}\label{sec:direct}

Direct approaches solve optimization problem~\eqref{eq:tclsrm} by
``transcribing" the infinite dimensional optimization problem into a finite
dimensional one by discretizing the state and objective functional in time.
The minimization problem is then reformulated as a (non)linear programming, or
optimization, problem. A variety of direct solution approaches exist, 
including collocation approaches, spectral  methods, and genetic algorithms.

In the context of \spatialAcronym\ trial subspaces, the most straightforward direct solution approach consists of the 
following steps: (1) numerically discretize the FOM ODE (and hence the
\textit{integrand} of the objective function in problem~\eqref{eq:obj_gen_slab}) and 
(2) select a numerical quadrature rule to evaluate the \textit{integral} in~\eqref{eq:obj_gen_slab}.
To this end, we define a time grids
$\{\timeWindowArg{n}{i}\}_{i=0}^{\nstepsArg{n}}\subseteq[\timeStartArg{n},\timeEndArg{n}]$,
$n=1,\ldots,\nslabs$ that
satisfy 
$\timeStartArg{n}=\timeWindowArg{n}{0} \le \cdots \le \timeWindowArg{n}{\nstepsArg{n}} 
 = \timeEndArg{n}$.
%\KTC{use cdots, not
%hdots or ldots. Don't use $\defeq$ for the first and last times; these are
%just equalities, i.e., you happen to set them equal to those values, but they
%aren't identically the same:}
Figure~\ref{fig:slab_fig2} depicts such a discretization.
We now outline the direct solution approach for linear-multistep schemes; we note that the formulation for
other time-integration methods (e.g., Runge--Kutta) follows closely. 
\begin{figure} 
\begin{centering} 
\includegraphics[trim={0.0cm 4.5cm 0cm 3cm},clip,width=1.0\textwidth]{figs/time_grid_timesteps.pdf} 
	\caption{Depiction of the $\nstepsArg{n}+1$ time instances over each window. In the figure, $\nstepsArg{n} = 2$ for all $n$.} 
\label{fig:slab_fig2} 
\end{centering} 
\end{figure}
%We now outline several commonly employed temporal discretization 
%schemes, specifically linear multistep and collocation (Runge--Kutta) methods, that leverage this time-grid to discretize the FOM ODE and 
%objective functional.

@@

\KTC{HERE} I use subscripts to denote iterations. Either is fine}

@@

\subsection{\spatialAcronym\ trial subspaces: indirect solution approach}\label{sec:indirect}
In contrast to the direct approach,
indirect methods ``indirectly" solve the minimization
problem~\eqref{eq:tclsrm} by solving the Euler--Lagrange equations. The
system given by the Euler--Lagrange equations~\eqref{eq:lspg_continuous}--\eqref{eq:lspg_adjoint} comprises a coupled two-point boundary value
problem. A variety of techniques have
been devised to solve two-point boundary value problems of this type. These
techniques include shooting methods, multiple shooting
methods~\cite{multiple_shooting}, and the forward--backward sweep
method~\cite{fbs} (FBSM).  This work explores using the FBSM.
